|

### 2020-12-06 appendix/appendix.Rmd
fix typo D5

Most of papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`). The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[1])`). Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[3])`). As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[2]`, while the number of papers is only `r length(unique(dat$id))`.

>>>>

Most papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`). The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[1])`). Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[3])`). As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[2]`, while the number of papers is only `r length(unique(dat$id))`.
